Interpreting Random Forest Predictions for Firearm Identification Using LIME

### 2018-11-20 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
created options in app to choose from the different LIME implementations and started working on handling the bin_continuous = FALSE case

@@

```{r}
hamby224_lime_mse <- hamby224_lime_comparisons %>%
  filter(!is.na(rfscore)) %>%
  group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
  summarise(mse = (sum(diff)^2) / length(diff)) %>%
  arrange(set)
```

```{r}
hamby224_lime_mse %>%
  group_by(set) %>%
  arrange(mse) %>%
  slice(1:2)
```

```{r}
hamby224_lime_mse %>%
  ggplot(aes(x = nbins, y = mse, color = quantile_bins, group = quantile_bins)) +
  geom_point() + 
  geom_line() + 
  facet_grid( ~ set) + 
  theme_bw()
```

@@

```{r fig.width = 8, fig.height = 4}
hamby224_lime_comparisons %>%
  filter(!is.na(rfscore), set == "Set 1") %>%
  ggplot(aes(x = rfscore, y = abs(diff))) + 
  geom_point(aes(color = model_r2)) + 
  facet_grid(nbins ~ set) +
  theme_bw()
```

```{r fig.width = 8, fig.height = 4}
hamby224_lime_comparisons %>%
  filter(!is.na(rfscore), set == "Set 11") %>%
  ggplot(aes(x = rfscore, y = abs(diff))) + 
  geom_point(aes(color = model_r2)) + 
  facet_grid(nbins ~ set) +
  theme_bw()
```

```{r fig.width = 8, fig.height = 4}
hamby224_lime_comparisons %>%
  filter(!is.na(rfscore), set == "Set 1") %>%
  ggplot(aes(x = rfscore, y = diff)) + 
  geom_point(aes(color = model_r2)) + 
  facet_grid(nbins ~ set) +
  geom_hline(yintercept = 0, color = "blue") +
  theme_bw()
```

```{r fig.width = 8, fig.height = 4}
hamby224_lime_comparisons %>%
  filter(!is.na(rfscore), set == "Set 11") %>%
  ggplot(aes(x = rfscore, y = diff)) + 
  geom_point(aes(color = model_r2)) + 
  facet_grid(nbins ~ set) +
  geom_hline(yintercept = 0, color = "blue") +
  theme_bw()
```

@@

```{r}
hamby224_test_explain %>%
  filter(set == "Set 1", nbins == "8") %>%
  mutate(rfscore = round(rfscore, 3)) %>%
  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
  distinct() %>%
  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,
             text = paste('Bullets Compared: ', bullet1, "-", land1, 
                          "vs", bullet2, "-", land2,
                          '\nRandom Forest Score: ', 
                          ifelse(is.na(rfscore), "Missing due to tank rash", rfscore)))) +
  geom_tile(aes(fill = rfscore)) +
  facet_grid(bullet2 ~ bullet1, scales = "free") +
  theme_minimal() +
  scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "", y = "", fill = "RF Score")
```

>>>>

```{r}
# Specify the options to use with lime 
hamby224_lime_no_bins_cases <- data.frame(bin_continuous = rep(FALSE, 2),
                                      quantile_bins = rep(TRUE, 2),
                                      nbins = rep(4, 2),
                                      use_density = c(TRUE, FALSE)) %>%
  mutate(case = 1:length(nbins)) %>%
  select(case, bin_continuous, nbins, quantile_bins, use_density)

# Run the lime functions for the specified number of bins
hamby224_no_bins_results <- pmap(.l = as.list(hamby224_lime_no_bins_cases[,-1]),
           .f = run_lime, # run_lime is one of my helper functions
           train = hamby173and252_train %>% select(rf_features),
           test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
           rfmodel = as_classifier(rtrees),
           label = "TRUE",
           nfeatures = 3)

# Separate the lime and explain function results
hamby224_lime_no_bins <- map(hamby224_no_bins_results, function(list) list$lime)
hamby224_explain_no_bins <- map_df(hamby224_no_bins_results, function(list) list$explain)
```

@@

```{r}
hamby224_lime_results <- hamby224_lime_comparisons %>%
  filter(!is.na(rfscore)) %>%
  group_by(bin_continuous, quantile_bins, nbins, use_density, set) %>%
  summarise(mse = (sum(diff)^2) / length(diff),
            ave_r2 = mean(model_r2)) %>%
  arrange(set)
```

```{r}
hamby224_lime_results %>%
  group_by(set) %>%
  arrange(mse) %>%
  slice(1:2)
```

```{r}
hamby224_lime_results %>%
  ggplot(aes(x = nbins, y = mse, color = quantile_bins, group = quantile_bins)) +
  geom_point() + 
  geom_line() + 
  facet_grid( ~ set) + 
  theme_bw()
```

```{r}
hamby224_lime_results %>%
  group_by(set) %>%
  arrange(ave_r2) %>%
  slice(1:2)
```

```{r}
hamby224_lime_results %>%
  ggplot(aes(x = nbins, y = ave_r2, color = quantile_bins, group = quantile_bins)) +
  geom_point() + 
  geom_line() + 
  facet_grid( ~ set) + 
  theme_bw()
```

@@

```{r fig.width = 8, fig.height = 4}
hamby224_lime_comparisons %>%
  filter(!is.na(rfscore), set == "Set 1") %>%
  ggplot(aes(x = rfscore, y = abs(diff))) + 
  geom_point(aes(color = model_r2)) + 
  facet_wrap( ~ nbins) +
  theme_bw()
```

```{r fig.width = 8, fig.height = 4}
hamby224_lime_comparisons %>%
  filter(!is.na(rfscore), set == "Set 11") %>%
  ggplot(aes(x = rfscore, y = abs(diff))) + 
  geom_point(aes(color = model_r2)) + 
  facet_wrap( ~ nbins) +
  theme_bw()
```

```{r fig.width = 8, fig.height = 4}
hamby224_lime_comparisons %>%
  filter(!is.na(rfscore), set == "Set 1") %>%
  ggplot(aes(x = rfscore, y = diff)) + 
  geom_point(aes(color = model_r2)) + 
  facet_wrap( ~ nbins) +
  geom_hline(yintercept = 0, color = "blue") +
  theme_bw()
```

```{r fig.width = 8, fig.height = 4}
hamby224_lime_comparisons %>%
  filter(!is.na(rfscore), set == "Set 11") %>%
  ggplot(aes(x = rfscore, y = diff)) + 
  geom_point(aes(color = model_r2)) + 
  facet_wrap( ~ nbins) +
  geom_hline(yintercept = 0, color = "blue") +
  theme_bw()
```

@@

```{r}
hamby224_test_explain %>%
  filter(set == "Set 1", nbins == "8") %>%
  mutate(rfscore = round(rfscore, 3)) %>%
  select(case, bullet1, bullet2, land1, land2, rfscore) %>%
  distinct() %>%
  bind_rows(hamby224_test_explain %>%
                  filter(is.na(rfscore), set == "Set 1") %>%
                  select(case, bullet1, bullet2, land1, land2, rfscore)) %>%
  ggplot(aes(x = land1, y = land2, label = bullet1, label2 = bullet2,
             text = paste('Bullets Compared: ', bullet1, "-", land1, 
                          "vs", bullet2, "-", land2,
                          '\nRandom Forest Score: ', 
                          ifelse(is.na(rfscore), "Missing due to tank rash", rfscore)))) +
  geom_tile(aes(fill = rfscore)) +
  facet_grid(bullet2 ~ bullet1, scales = "free") +
  theme_minimal() +
  scale_fill_gradient2(low = "darkgrey", high = "darkorange", midpoint = 0.5) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "", y = "", fill = "RF Score")
```
